Program Transformations for miniKanren

### 2020-07-06 papers/aplas/text/conclusion.tex
Evaluation intro section rewritten
Conclusion rewritten

In this paper, we discussed some issues which arise in partial deduction of a relational programming language \mk{}.
We presented a novel approach to partial deduction which uses a heuristic to select the most suitable relation call to unfold at each step of driving.
We compared this approach to the earlier implementation of conjunctive partial deduction.
Our evaluation showed that there is still not one good technique which definitively speeds up every relational program.

>>>>

In this paper we discussed some issues which arise in the area of partial deduction techniques for relational programming language \mk.
We presented a novel approach to partial deduction --- conservative partial deduction --- which uses a heuristics to select a suitable relation call to unfold at each step of driving.
We compared this approach with the most sophisticated implementation of conjunctive partial deduction --- \ecce partial deduction system --- on 10 relations which solve 6 different problems.

Our specializer improved the execution time of 10 queries to the  relations, while worsening 2 queries and not affecting one query.
\ecce worsened the performance of all 4 implementations of the propositional evaluator relation, while improving other queries.
Conservative PD is more stable with regrads to the order of relation calls than \ecce which is demonstrated by the similar performance of all 4 implementations of the evaluator of logic formulas.

Some queries to the same relation were improved better by ConsPD, while others --- by \ecce.
We conclude that there is still no one good technique which definitively speeds up every relational program.
More research is needed to develop models capable of predicting the performance of a relation which can be used in specialization.

### 2020-07-06 papers/aplas/text/figures/heuristic.tex
Conclusion rewritten

\thispagestyle{empty}
\begin{figure}[h]
\begin{PseudoCode}[moredelim={[is][stringstyle]{@@}{@@}},
  moredelim={[is][\color{dkgreen}\bfseries]{@!}{@!}},
  moredelim={[is][\color{red}\bfseries]{!!}{!!}}]
heuristically_select_a_call :: Conjunction @*$\to$@* Maybe Call
heuristically_select_a_call C = find heuristic C

heuristic :: Call @*$\to$@* Bool
heuristic r = isStatic r || isDeterministic r || isLessBranching r
\end{PseudoCode}
\end{figure}

>>>>

\thispagestyle{empty}
\begin{figure}[h]
\begin{PseudoCode}[moredelim={[is][stringstyle]{@@}{@@}},
  moredelim={[is][\color{dkgreen}\bfseries]{@!}{@!}},
  moredelim={[is][\color{red}\bfseries]{!!}{!!}}]
heuristically_select_a_call :: Conjunction @*$\to$@* Maybe Call
heuristically_select_a_call C = find heuristics C

heuristics :: Call @*$\to$@* Bool
heuristics r = isStatic r || isDeterministic r || isLessBranching r
\end{PseudoCode}
\end{figure}
